Twisted \(M\)-theory and its perturbative quantization.

### 2020-11-24 paper.tex

\section{Quantization of holomorphic-topological theories}
\label{sec:org297a559}
\subsection{Effective renormalization}
\label{sec:orga5cd4ed}
\subsection{The \(11\)-dimensional theory}
\label{sec:org8b189fc}
\subsection{The moduli space of quantizations}
\label{sec:orgf278b4e}
\section{Relationship to the Type IIA string}
\label{sec:org355a726}

Let $TX$ denote the holomorphic tangent bundle and define
\[
\pv^{i,j}(X) \define \Omega^{0,j}(X, \wedge^{i} TX) .\]
This is the space of $i$-pvvectors of Dolbeault type $j$.
Using the $\dbar$ operator for the holomorphic bundle $\wedge^{i}TX$ we obtain a cochain complex $\pv^{i,\bu}(X) = \left(\oplus_{j} \pv^{i,j}(X) [-j], \dbar \right)$ which provides a free resolution of the sheaf of holomorphic polyvector fields of type $i$.

>>>>

\section{Quantization of holomorphic-topological theories}
\label{sec:org297a559}
\subsection{Effective renormalization}
\label{sec:orga5cd4ed}
\subsection{The \(11\)-dimensional theory}
\label{sec:org8b189fc}
\subsection{The moduli space of quantizations}
\label{sec:orgf278b4e}
\section{Relationship to the Type IIA string}
\label{sec:org355a726}
In the remainder of the paper, we wish to establish various consistency checks corroborating the claim that the 11d theory of interest describes a twist of 11d supergravity. In this section, we demonstrate that this claim is consistent with a conjectural description of a twist of type IIA supergravity due to \cite{}.

Before recalling this conjecture, we first fix some notation. For a complex manifold $X$, let $TX$ denote the holomorphic tangent bundle and define
\[
\pv^{i,j}(X) \define \Omega^{0,j}(X, \wedge^{i} TX) .\]
This is the space of $i$-pvvectors of Dolbeault type $j$.
Using the $\dbar$ operator for the holomorphic bundle $\wedge^{i}TX$ we obtain a cochain complex $\pv^{i,\bu}(X) = \left(\oplus_{j} \pv^{i,j}(X) [-j], \dbar \right)$ which provides a free resolution of the sheaf of holomorphic polyvector fields of type $i$.
